\documentclass[11pt]{article}

\usepackage{a4wide}
\usepackage{mathptm}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{shapes.misc, positioning}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx} % For table

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\begin{document}

\title{Implementing Secure Authentication: A Comparison of OAuth 2.0 and Basic Authentication}

\author{Kristian E. Takvam and Lars Magnus Nordeide}

\maketitle

\begin{abstract}
%Abstract: 10-15 lines with the software technology and the highlights from the project that has been undertaken.
This project focuses on designing and building FeedApp, a web application that allows users to create and participate in surveys and polls. The app is developed using a modern technology stack, with OAuth 2.0 integrated for secure user authentication and token-based authorization, ensuring a safe and smooth experience for users. The backend is powered by Spring Boot and Spring Web MVC, providing a reliable RESTful API, while the frontend, built with Svelte and Vite, delivers a fast and responsive Single Page Application (SPA).

The application is based on a well-structured domain model that defines the relationships between key entities like users, surveys, polls, and votes. PostgreSQL and MongoDB are used to handle structured and unstructured data effectively, and RabbitMQ is included for efficient communication between different parts of the system. The use of Docker helps with deployment and scalability, making it easier to manage and run the application in different environments.

As part of this project, an evaluation was conducted to compare OAuth 2.0 with Basic Authentication and API Keys. Experiments were run to test scalability, ease of implementation, and security. The results showed that OAuth 2.0 performs better in handling high user loads, provides advanced security features like token expiration and scope control, and is flexible enough to work well with third-party systems. These findings make OAuth 2.0 an excellent choice for scalable and secure web applications.

Overall, this project highlights how a modern, scalable architecture can provide a secure and user-friendly platform for collaborative participation in surveys and polls. It demonstrates the importance of choosing the right technologies to ensure both performance and security in web application development.

\end{abstract}

%\input{commands}

\input{sections/introduction}

\input{sections/design}

\input{sections/technology}


\input{sections/implementation}


\input{sections/conclusion}

\bibliographystyle{plain}
\bibliography{report.bib}{}

\end{document}
